An Adolescent Mini-Neptune in the Kepler Field

### 2021-06-21 paper/ms.tex
add ttv vs local slope analysis

\begin{abstract}
  Kepler\,1627A is an active G8V star previously found to host a
  $3.6\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  selected for observation by the Kepler satellite because it is
  nearby ($d\approx 333\,{\rm pc}$) and resembles the Sun.  Combining
  data from Gaia with rotation periods from TESS, we
  show that Kepler\,1627 is a member of the $35\pm XX$\,Myr old
  $\delta$~Lyr cluster.  Our analysis advances Kepler\,1627Ab as the
  youngest planet with a precise age found by the main Kepler
  mission.  
  Leveraging the corresponding photometry, we explore the possibility
  that star-planet interactions induce flares in the system, and find
  evidence that starspot crossings distort the average transit shape.
  More broadly though, the merging of Gaia and TESS data offers an
  opportunity to significantly expand the census of age-dated planets;
  we provide a literature concatenation of young stars to support this
  effort.
  In the future, spectroscopic studies of \pn\ may also help clarify
  how the orbits and atmospheres of the mini-Neptune planets evolve.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{TEMP_Prot_vs_BpmRp.png}
			\includegraphics[width=0.49\textwidth]{TEMP_hrd.png}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf \cn is $35\pm15$\,Myr old.} {\it Left:} TESS and
    Kepler rotations periods and dereddened Gaia colors, with the
    Pleiades \citep[125\,Myr;][]{rebull_rotation_2016a} and Praesepe
    \citep[650\,Myr;][]{douglas_poking_2017} shown for reference.
    Stars of a given color (mass) move up through time due to magnetic
    braking.  The \cn\ has a 40 Myr gyrochronal age, as calibrated
    against the LDB-age of IC\,2602.  {\it Right:} HR diagram of the
    same comparison. {\bf todo: caption improve}.
   \label{fig:age}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Zoomed view of the \sn\ light curve.}  
		The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
		30 minute cadence.  A one hundred day segment is shown here.  The {\it top panel} shows the
		\texttt{PDCSAP} median-subtracted flux in units of
		parts-per-thousand ($\times 10^{-3}$).  The dominant signal
		is induced by starspots and plages.  The model for the
		stellar variability (orange line) is subtracted in the {\it
			bottom panel}, revealing the transits of \pn, as well as other
		deviations from the stellar variability model.  The 
		Figure Set available online shows the entire 3.9 years of
		available data.
		\label{fig:lightcurve}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded transit of Kepler 1627b, with stellar
			variability removed.}  
    The 1-$\sigma$ model uncertainties and the maximum {\it a
    posteriori} model are shown as the faint purple band, and the dark
    purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.
    {\bf LGB FIXME: seems like the uncertainty is bigger than the RMS
    in the out of transit...}
		\label{fig:phasefold}
	}
\end{figure*}

@@

While we have yet to perform an in-depth planet search of the {\bf
XXX} light curves Kepler acquired for the \cn, there is already a
known planet in the cluster: Kepler\,1627b.  We considered the
planet's previous statistical validation by \citet{morton_false_2016}
to be sufficient cause to examine the age of the star and its cluster more closely.
We collected the previously measured {\bf XXX} Kepler
rotation periods (CITEP MCQUILLAN2014), and measured {\bf YYY} new stellar
rotation periods for cluster members observed by TESS.
We also performed an isochronal analysis.
The results are shown in Figure~\ref{fig:age}.
From the ensemble perspective, which provides the strongest
constraints (SEE CITET SODERBLOM 2014),
the age of the star is $XX \pm YY$\,Myr.
Individual measurements of the star's rotation period and lithium
abundance corroborate this conclusion.

If the Kepler\,1627b transit signal truly corresponds to a planet,
this age would make it the youngest planet yet found by the main
Kepler mission.  A portion of the light curve is shown in
Figure~\ref{fig:lightcurve}, and the phase-folded transit is shown in
Figure~\ref{fig:phasefold}.  The dominant signal in the
\texttt{PDCSAP} photometry is a quasi-period starspot signal with a
peak-to-peak amplitude that varies between roughly 2\% and 8\%,
depending on the degree of asymmetry in spot coverage between the
stellar hemispheres.  The starspot signal repeats roughly every
2.606\,days, though this value varies by a few percent depending on
which portion of the light curve is analyzed {\bf (FIXME: do!)}.  The
details of how we model this signal to derive the parameters of the
planet are discussed in Section~\ref{app:gptransit}.  The results,
given in Table~\ref{tab:posterior}, are consistent with a mini-Neptune
sized planet ($3.56\pm 0.04\,R_\oplus$) on a circular 7.2\,day orbit,
around a G8V star ($0.91 \pm 0.05 R_\odot$) {\bf fixme: age}.

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} considered
the various false positive scenarios, including those of a foreground
eclipsing binary, a hierarchical triple-star binary system, and a
background eclipsing binary.  \citet{morton_false_2016} reported the
latter scenario to be the only possible case, with a (model-dependent)
probability of $\approx10^{-5}$.  While this statistical validation is
reassuring, ``validated'' planets have been demonstrated to be false
positives \citep{shporer_three_2017}.  Most failures of the
statistical validation approach arise when attempting to separate the
smallest stars from identically-sized gas giant planets (CITE).  With a size
of $\approx 3.6\,R_\oplus$, Kepler\,1627b does not meet this
concern.  The fact that we detect a low-mass stellar companion in
archival Keck-NIRC2 Kp-band (2.12\,$\mu $m) imaging does not change
the conclusion: the companion contributes 1\% of the flux
observed by Kepler, which combined with the observed transit shape
cannot be invoked as an explanation for the observed data
(Section~\ref{app:companionstar}).

@@

Kepler\,1627Ab therefore provides an interesting extremum in the ages
of the Kepler planets, and opens multiple avenues for study from the
ground.  Observations of its Doppler transit ($\Delta v_{\rm RM}
\approx 20$\ms) with HIRES or the upcoming KPF spectrograph could
yield a measurement of its orbital obliquity (CITEP,CITEP).
Similarly, transit spectroscopy aimed at detecting either hydrogen or
helium absorption could yield insight into the planet's atmosphere,
which is expected to be outflowing at a rate of {\bf
X.X}\,$M_\oplus\,{\rm yr}^{-1}$ (CITE).  A more challenging
measurement would be a measurement of the planet's mass, through
either detailed timing analyses of the Kepler data, or through a
high-cadence multi-color radial velocity campaign.  The mass would
yield constraints on both the planet's composition (``what is the
extent of the initial gaseous envelope for a typical mini-Neptune?''),
as well as its initial entropy (``hot'' or ``cold''? CITE).

The precision of the Kepler data itself may enable more detailed
analyses without even needing to acquire more data.  These could
include studies transit timing variations, distortion of the transit
signal due to the star's gravity darkening, and interactions between
the star and planet exhibited by patterns in the star's flaring.
The gravity darkening might be interesting as an explanation for the
$\approx80\,{\rm ppm}$ residual apparent in our transit fit.
On the point of planet-induced flaring, Appendix REFERENCE
highlights an odd timing coincidence that may be worthy of further
examination.

Ultimately though, our age measurement for Kepler\,6127Ab was enabled by
identifying its connection to the \cn\ through the Gaia data.  The
Supplementary Table~\ref{tab:v05} enables similar crossmatches to
already known planets, as well as forthcoming planets from the TESS
mission (CITE RickerJATIS2014).  An alternative approach also
likely to bear fruit is to identify kinematic associations
around exoplanet host stars using the Gaia data, and to then verify
these associations with ancilliary rotation periods and spectroscopy
(CITEP Tofflemire).

@@

L.G.B{.} and J.L.C{.} are grateful to T{.}~David for help with the
transit fitting, and to R{.}~Kerr for kindly providing us with the
\citet{Kerr2021} membership list prior to its publication.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support by the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
L.G.B{.} was also supported by a Charlotte Elizabeth Procter
Fellowship from Princeton University.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
Association of Universities for Research in Astronomy (AURA) under a
cooperative agreement with the National Science Foundation.
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Transit model residuals through time}.  
    {\it Left:}
		Phase-folded transit of Kepler 1627b, with stellar
    variability removed, binned by Kepler quarter.
    Black points are binned to 20 minute intervals.
    The 1-$\sigma$ model uncertainties and the maximum {\it a
    posteriori} model are shown as the faint purple band, and the dark
    purple line.
    {\it Right:}
    As on the left, with the transit removed.
    Quarters 6 and 7 show a consistent deviation in the second half of
    the transit.
		\label{fig:phasequarter}
	}
\end{figure*}

@@

This could provide a plausible path to creating the distorted transit
signal, based on the amplitudes involved.  However, the typical S/N
per Kepler transit is $\approx8$, and so the individual spot-crossing
events cannot be resolved.  {\it A priori}, one would also expect the
spot-crossing events to not have a preferred phase, so that they would
average out over the $\approx200$ Kepler transits.  Nonetheless, given
the available data, it is our best explanation for what we believe is
real additional scatter during the transits, relative to the
out-of-transit observations.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Flares in Kepler\,1627}.  
    {\it Top:}
    The full short-cadence Kepler dataset, acquired at 1-minute
    sampling (black points) is shown with a stellar variability model
    (blue line).
    {\it Middle:}
    Residual after subtracting the stellar variability model.  Flares
    appear as spikes.
    {\it Bottom:}
    Zooms of the brightest, and third-brightest flares.  A timing
    coincidence -- that both flares has ``successors'' approximately
    one orbital period after the initial event -- is emphasized.
		\label{fig:flarezoom}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1.0\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded flares in Kepler\,1627}.  
    {\it Top:}
    As in the middle of Figure~\ref{fig:flarezoom}, phase-folded at
    the planet's ephemeris.
    {\it Bottom:}
    Fitted flare amplitudes and orbital phases.
    Colors indiate relative time, from the beginning of the
    98-day short-cadence Q15 dataset (dark blue) to the end (light
    yellow).
    Lower amplitude flares likely exist in the data, and were not
    examined.
		\label{fig:flarephase}
	}
\end{figure*}

The 1-minute cadence Kepler observations span 98 days, and cover 24
flares exceeding $0.5\%$ in relative flux.  These 24 flares spanned a
total of 6.5 hours ($\sim$15 minutes per flare).  The coincidence is
that despite the low flare duty cycle, one orbital period after the
the brightest flare, a second flare followed.  This and a similar
event are shown in Figure~\ref{fig:flarezoom}.  The timing error is
good to a $\approx0.2\%$ difference from the orbital period, which
seems {\it a priori} unlikely.  If we consider flares falling within
2\% of the planet's orbital period after a previous flare, then 4 of
the 24 flare events have candidate ``successors''.

>>>>

\begin{abstract}
  Kepler\,1627A is a G8V star previously found to host a
  $3.6\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  selected for observation by the Kepler satellite because it is
  nearby ($d\approx 333\,{\rm pc}$) and resembles the Sun.  Combining
  data from Gaia with rotation periods from TESS, we show that
  Kepler\,1627 is a member of the $35\pm XX$\,Myr old $\delta$~Lyr
  cluster.  Our analysis advances Kepler\,1627Ab as the youngest
  planet with a precise age found by the main Kepler mission.
  Analyzing the photometry, we find evidence that starspot crossings
  {\it i)} distort the average transit shape, and {\it ii)} induce
  transit timing variations that suggest the planet is on a prograde
  orbit.  The possibility that star-planet interactions could induce
  flares in the system is also explored.  Future spectroscopic studies
  of \pn\ may help clarify the early evolution of the orbit and
  atmosphere for this mini-Neptune.  More generally, the merging of
  Gaia and TESS data offers an opportunity to significantly expand the
  census of age-dated planets; we provide a literature concatenation
  of young stars to support this effort.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{TEMP_Prot_vs_BpmRp.png}
			\includegraphics[width=0.49\textwidth]{TEMP_hrd.png}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is $35\pm15$\,Myr old.} {\it Left:} TESS and
    Kepler rotations periods and dereddened Gaia colors, with the
    Pleiades \citep[125\,Myr;][]{rebull_rotation_2016a} and Praesepe
    \citep[650\,Myr;][]{douglas_poking_2017} shown for reference.
    Stars of a given color (mass) move up through time due to magnetic
    braking.  The \cn\ has a 40 Myr gyrochronal age, as calibrated
    against the LDB-age of IC\,2602.  {\it Right:} HR diagram of the
    same comparison. {\bf todo: caption improve}.
   \label{fig:age}
	}
\end{figure*}

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=1\textwidth]{f4.pdf}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{
% 		{\bf Zoomed view of the \sn\ light curve.}  
% 		The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
% 		30 minute cadence.  A one hundred day segment is shown here.  The {\it top panel} shows the
% 		\texttt{PDCSAP} median-subtracted flux in units of
% 		parts-per-thousand ($\times 10^{-3}$).  The dominant signal
% 		is induced by starspots.  The model for the
% 		stellar variability (orange line) is subtracted in the {\it
% 			bottom panel}, revealing the transits of \pn, as well as other
% 		deviations from the stellar variability model.  The 
% 		Figure Set available online shows the entire 3.9 years of
% 		available data.
% 		\label{fig:lightcurve}
% 	}
% \end{figure*}
% 
% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=1\textwidth]{f5.pdf}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{
% 		{\bf Phase-folded transit of Kepler 1627b, with stellar
% 			variability removed.}  
%     The 1-$\sigma$ model uncertainties and the maximum {\it a
%     posteriori} model are shown as the faint purple band, and the dark
%     purple line.  Gray points are individual \texttt{PDCSAP} flux
%     measurements; black points are binned to 20 minutes, with a
%     representative error bar shown.
%     {\bf LGB FIXME: seems like the uncertainty is bigger than the RMS
%     in the out of transit...}
% 		\label{fig:phasefold}
% 	}
% \end{figure*}

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.9\textwidth]{f4.pdf}
			\includegraphics[width=0.9\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
		The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
		30 minute cadence.  A one hundred day segment is shown here.  The {\it top panel} shows the
		\texttt{PDCSAP} median-subtracted flux in units of
		parts-per-thousand ($\times 10^{-3}$).  The dominant signal
		is induced by starspots.  The model for the
    stellar variability (orange line) is subtracted below, revealing
    the transits of \pn, as well as other deviations from the stellar
    variability model.  The Figure Set available online shows the
    entire 3.9 years of available data.
    {\it Bottom}:
		Phase-folded transit of Kepler 1627b, with stellar
			variability removed.
    The 2-$\sigma$ model uncertainties and the maximum {\it a
    posteriori} model are shown as the faint purple band, and the dark
    purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.
    The in-transit variation is robust against detrending methods; we
    believe it is due to starspot crossings (see text).
    \label{fig:lc}
  }
\end{figure*}

@@

While we have yet to perform an in-depth planet search of the {\bf
XXX} light curves Kepler acquired for the \cn, there is already a
known planet in the cluster: Kepler\,1627b.  Given the
planet's previous statistical validation by \citet{morton_false_2016},
we decided to examine the age of the star and its cluster more closely.
We collected the previously measured {\bf XXX} Kepler
rotation periods (CITEP MCQUILLAN2014), and measured {\bf YYY} new stellar
rotation periods for cluster members observed by TESS.
We also performed an isochronal analysis.
The results are shown in Figure~\ref{fig:age}.
From the ensemble perspective, which provides the strongest
constraints (SEE CITET SODERBLOM 2014),
the age of the star is $XX \pm YY$\,Myr.
Individual measurements of the star's rotation period and lithium
abundance corroborate this conclusion.

If the Kepler\,1627b transit signal is created by a bonafide planet,
this age would make it the youngest planet yet found by the main
Kepler mission.  A portion of the light curve is shown in
Figure~\ref{fig:lightcurve}, and the phase-folded transit is shown in
Figure~\ref{fig:phasefold}.  The dominant signal in the
\texttt{PDCSAP} photometry is a quasi-period starspot signal with a
peak-to-peak amplitude that varies between roughly 2\% and 8\%,
depending on the degree of asymmetry in spot coverage between the
stellar hemispheres.  The starspot signal repeats roughly every
2.606\,days, though this value varies by a few percent depending on
which portion of the light curve is analyzed {\bf (FIXME: do!)}.  The
details of how we model this signal to derive the parameters of the
planet are discussed in Section~\ref{app:gptransit}.  The results,
given in Table~\ref{tab:posterior}, are consistent with a mini-Neptune
sized planet ($3.56\pm 0.04\,R_\oplus$) on a circular 7.2\,day orbit,
around a G8V star ($0.91 \pm 0.05 R_\odot$) {\bf fixme: age}.

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} considered
the false positive scenarios of a foreground
eclipsing binary, a hierarchical triple-star binary system, and a
background eclipsing binary.  \citet{morton_false_2016} reported the
latter scenario to be the only possible case, with a (model-dependent)
probability of $\approx10^{-5}$.  While this statistical validation is
reassuring, ``validated'' planets have been demonstrated to be false
positives \citep{shporer_three_2017}.  Most failures of the
statistical validation approach arise when attempting to separate the
smallest stars from identically-sized gas giant planets.  With a size
of $\approx 3.6\,R_\oplus$, Kepler\,1627b does not meet this
concern.
The fact that we detect a low-mass stellar companion in
archival Keck-NIRC2 Kp-band (2.12\,$\mu $m) imaging does not change
the conclusion: the companion contributes 1\% of the flux
observed by Kepler, which combined with the observed transit shape
cannot be invoked as an explanation for the observed data
(Section~\ref{app:companionstar}).

Two additional lines of evidence ultimately persuaded us in favor of
the planetary interpretation.  First, the $\approx$100 days of
1-minute short-cadence data enables a more precise measurement of the
transit impact parameter: {\bf todo numbers} it is constrained to be
$<0.62$ (3-$\sigma$) from the 1-minute cadenced data, compared to
$<0.XX$ (3-$\sigma$) from the 30-minute data.  The second, and
ultimately convincing line of evidence came from our transit timing
analysis.  {\bf todo: KM pls check numbers} We isolated each of the
144 observed transits to within $\pm4.5$\,hr of each transit, and
fitted each window with both {\it i)} a local second-order polynomial
and transit, and {\it ii)} a local linear trend.  We let the mid-time
of each transit float, and then calculated the residual between the
measured mid-time and that of a perfectly periodic orbit.  This
residual, the ``transit timing variation'' (TTV), is plotted in
Figure~\ref{fig:ttvslope} against the local linear slope.  Only a
handful of Kepler Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which is most readily interpreted as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.  
This is of course only possible if the planet is transiting the
primary star, which excludes the any of the aforementioned false
positive scenarios.
It also implies that the planet's orbit is prograde.  The latter
interpretation assumes that the dominant
photometric variability is induced by dark spots, rather than bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes, we expect this
inference to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit from transit timing variations.}
    The time of each transit was measured, along with the local linear
    slope.  The two quantities are anti-correlated, which is most
    easily explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.
		\label{fig:ttvslope}
	}
\end{figure*}

@@

In short, Kepler\,1627Ab provides an interesting extremum in the ages
of the Kepler planets, and opens multiple avenues for study from the
ground.  Observations of its Doppler transit ($\Delta v_{\rm RM}
\approx 20$\ms) with HIRES or the upcoming KPF spectrograph could
yield a quantification of the stellar obliquity, and a means for
verifying the suggestion of a prograde order from transit timing
(CITEP,CITEP).  Similar transit spectroscopy aimed at detecting either
hydrogen or helium absorption could yield insight into the planet's
atmosphere, which is expected to be outflowing at a rate of {\bf
X.X}\,$M_\oplus\,{\rm yr}^{-1}$ (CITE).  A more challenging
measurement would be a measurement of the planet's mass, through
either detailed timing analyses of the Kepler data, or through a
high-cadence multi-color radial velocity campaign.  The mass would
yield constraints on both the planet's composition (``what is the
extent of the initial gaseous envelope for a typical mini-Neptune?''),
as well as its initial entropy (``hot'' or ``cold''? CITE).

The precision of the Kepler data itself may enable more detailed
analyses without even needing to acquire more data.  While our transit
timing study did not yield the detection of any clearly significant
planet-induced TTVs, the star's flaring may be suggestive of
star-planet interactions.  Appendix REFERENCE highlights an odd flare
timing coincidence that may be worthy of further examination.

Ultimately though, our age measurement for \pn\ was enabled
by identifying its connection to the \cn\ through the Gaia data.  The
Supplementary Table~\ref{tab:v05} enables similar crossmatches to
already known planets, as well as forthcoming planets from the TESS
mission (CITE RickerJATIS2014).  An alternative approach also likely
to bear fruit is to identify kinematic associations around exoplanet
host stars using the Gaia data, and to then verify these associations
with ancilliary rotation periods and spectroscopy (CITEP Tofflemire).

@@

L.G.B{.} and J.L.C{.} are grateful to T{.}~David for help with the
transit fitting, to R{.}~Kerr for kindly providing us with the
\citet{Kerr2021} membership list prior to its publication, and to
K.~Masuda for advice on gravity darkening.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support by the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
L.G.B{.} was also supported by a Charlotte Elizabeth Procter
Fellowship from Princeton University.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
Association of Universities for Research in Astronomy (AURA) under a
cooperative agreement with the National Science Foundation.
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%

@@

\subsection{Long Cadence Data}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Transit model residuals through time}.  
    {\it Left:}
		Phase-folded transit of Kepler 1627b, with stellar
    variability removed, binned by Kepler quarter.
    Black points are binned to 20 minute intervals.
    The 1-$\sigma$ model uncertainties and the maximum {\it a
    posteriori} model are shown as the faint purple band, and the dark
    purple line.
    {\it Right:}
    As on the left, with the transit removed.
    Quarters 6 and 7 show a consistent deviation in the second half of
    the transit.
		\label{fig:phasequarter}
	}
\end{figure*}

@@

This could provide a plausible path to creating the distorted transit
signal, based on the amplitudes involved.  However, the typical S/N
per Kepler transit is $\approx8$, making individual spot-crossing
unresolved, and this scenario challenging to test.  {\it A priori},
one would also expect the spot-crossing events to not have a preferred
orbital phase, so that they would average out over the $\approx200$
Kepler transits.  Nonetheless, given the available data, it is our
best explanation for what we believe is real additional photometric
scatter observed during the transits.

\subsection{Short Cadence Data}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f12.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded short cadence transit of Kepler\,1627 Ab}.  
    The precision with which the impact parameter can be measured is
    higher than from the long cadence data.
		\label{fig:phase_slc}
	}
\end{figure*}

Figure~\ref{fig:phase_slc} shows the result from analyzing 100 days of
short cadence (1-minute) data acquired during Quarter 15.
%TODO: get quantitative on better impact parameter...

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Flares in Kepler\,1627}.  
    {\it Top:}
    The full short-cadence Kepler dataset, acquired at 1-minute
    sampling (black points) is shown with a stellar variability model
    (blue line).
    {\it Middle:}
    Residual after subtracting the stellar variability model.  Flares
    appear as spikes.
    {\it Bottom:}
    Zooms of the brightest, and third-brightest flares.  A timing
    coincidence -- that both flares have ``successors'' approximately
    one orbital period after the initial event -- is emphasized.
		\label{fig:flarezoom}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1.0\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded flares in Kepler\,1627}.  
    {\it Top:}
    As in the middle of Figure~\ref{fig:flarezoom}, phase-folded at
    the planet's ephemeris.
    {\it Bottom:}
    Fitted flare amplitudes and orbital phases -- each point
    represents one flare.
    Colors indicate relative time, from the beginning of the
    98-day short-cadence Quarter 15 dataset (dark blue) to the end (light
    yellow).
    Lower amplitude flares likely exist in the data, and were not
    examined.
		\label{fig:flarephase}
	}
\end{figure*}

The 1-minute cadence Kepler observations span 98 days, and cover 24
flares exceeding $0.5\%$ in relative flux.  These 24 flares spanned a
total of 6.5 hours ($\sim$15 minutes per flare).  The coincidence is
that despite the low flare duty cycle, one orbital period after the
brightest flare, a second flare followed.  This and a similar
event are shown in Figure~\ref{fig:flarezoom}.  The timing error is
good to a $\approx0.2\%$ difference from the orbital period, which
seems {\it a priori} unlikely.  If we consider flares falling within
2\% of the planet's orbital period after a previous flare, then 4 of
the 24 flare events have candidate ``successors''.
